### 2018-07-05 paper/7-related.tex
Address suggestions of reviewers
Add Dune

\item \Pluto~\cite{erdweg2015pluto} is based on a similar model to \Shake, but
additionally allows cyclic build rules combined with a user-specific resolution
strategy. Often such a strategy can be unfolded into the user rules without loss
of precision, but a fully general resolution handler extends the \hs{Task}
abstraction with additional features.
\end{itemize}

@@

%TODO: Add a reference to the paper about forall f. c f => (k -> f v) -> f a
\begin{minted}[xleftmargin=10pt]{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}
\noindent
provided we instantiate \hs{p} to something like
\hs{k}~\hs{->}~\hs{f}~\hs{v}~--~which many of the actual instances in that paper
do. The properties of such optics are well studied, and the functions like
\hs{dependencies} are very much based on observations from that field of work.
Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file
is an input, without complicating other aspects of our definition. Furthermore,
the \hs{Build} abstraction lacks any further such symmetry.

>>>>

\item \Pluto~\cite{erdweg2015pluto} is based on a similar model to \Shake, but
additionally allows cyclic build rules combined with a user-specific resolution
strategy. Often such a strategy can be unfolded into the user rules without loss
of precision, but a fully general resolution handler extends the \hs{Task}
abstraction with additional features.

\item \Dune~\cite{dune} is a build system designed for OCaml/Reason projects.
Its distinguishing feature is that it uses
\emph{arrows}~\cite{hughes2000generalising} rather than monads to model
dynamic dependencies, which simplifies static dependency approximation.
\end{itemize}

@@

%TODO: Add a reference to the paper about forall f. c f => (k -> f v) -> f a
\begin{minted}[xleftmargin=10pt]{haskell}
type Optic p a b s t = p a b -> p s t
\end{minted}
\noindent
provided we instantiate \hs{p}~\hs{a}~\hs{b} to something like
\hs{k}~\hs{->}~\hs{f}~\hs{v}~--~which many of the actual instances in that paper
do. The properties of such optics are well studied, and the functions like
\hs{dependencies} are very much based on observations from that field of work.
Alas, we have been unable to remove the \hs{Maybe} used to encode whether a file
is an input, without complicating other aspects of our definition. Furthermore,
the \hs{Build} abstraction lacks any further such symmetry.
